---
title: "r day 1 nb"
output: html_notebook
---

## Homework

1.  Create an array of two 3x3 matrices from the given vectors.

    ```{r}
    vec1 <- c(1, 2, 3, 4, 5, 6, 7, 8, 9) 
    vec2 <- c(10, 11, 12, 13, 14, 15, 16, 17, 18) 
    mat1 <- matrix(vec1, nrow = 3) 
    mat2 <- matrix(vec2, nrow = 3) 
    mat_array <- array(c(mat1, mat2), dim = c(3, 3, 2)) 
    print(mat_array)
    ```

2.  In the above matrix that you created, print the value 5 by indexing in to the matrix.

    ```{r}
    value <- mat_array[2,2,1] 
    print(value)
    ```

3.  Print the third row of the first matrix.

    ```{r}
    row_3 <- mat_array[3,,1] 
    print(row_3)
    ```

4.  Print the second column of both matrices.

    ```{r}
    m1c2 <- mat_array[,2,1] 
    m2c2 <- mat_array[,2,2] 
    print(m1c2) 
    print(m2c2)
    ```

5.  Create two strings with your first and last name, respectively. Then concatenate them, and print the new value as "My name is \<your newly created concatenated variable will go here\>"

    ```{r}
    first_name <- 'Vaidic' 
    last_name <- 'Trivedi' 
    full_name <- paste(first_name, last_name) 
    sprintf('My name is %s',full_name)
    ```

6.  What values can a BOOLEAN contain?

    ```{r}
    print('BOOL type values include: TRUE and FALSE')
    ```
